---
title: "UFC Data Visualisation"
author: "Group Study 14"
date: "`r Sys.Date()`"
output: 
    html_document:
      number_sections: true
      highlight: haddock
      theme: spacelab
      toc: yes
      toc_depth: 2
      toc_float:
        collapsed: false
      fontzize: 10pt
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(dplyr)
library(janitor)
library(fastDummies)
library(GGally)
library(lubridate)
library(ggradar)
require(Hmisc)
require(digest)
require(cluster)    
require(factoextra) 
library(gridExtra)
library(fmsb)
library(ggiraph)
library(moonBook)
library(reshape2)
library(sjmisc)
library(ggiraphExtra)
library(scales)
library(extrafont)
library(ggplot2)

```

# Introduction: The Story Behind UFC



# Data Cleaning and Processing

```{r}
data <- read_csv("data.csv")
clean_names(data) 
data <- data %>% 
  mutate(women = ifelse(grepl("Women", weight_class), TRUE, FALSE))

fight_data <- data %>% 
  dplyr::select(1:9) 

#Splitting into men and Women
data_men <- data %>% 
  subset(women == FALSE)
data_women <- data %>% 
  subset(women == TRUE)

#Splitting data into Fight and Fighter Data
blue_profile_data <- data_men %>% 
  dplyr::select(Referee, date, location, starts_with("B_")) %>% 
  mutate(color = "blue")
  
red_profile_data <- data_men %>% 
  dplyr::select(Referee, date, location, starts_with("R_")) %>% 
  mutate(color = "red")

#Cleaning column names
names(blue_profile_data) <- ifelse(grepl("B_", names(blue_profile_data)), substring(names(blue_profile_data), 3), names(blue_profile_data))

names(red_profile_data) <- ifelse(grepl("R_", names(red_profile_data)), substring(names(red_profile_data), 3), names(red_profile_data))

#Unifying the Fighter Datasets
fighter_profile_data <- rbind(blue_profile_data, red_profile_data) %>%
  mutate(Stance = as.factor(Stance)) %>% 
  rename(win_by_ko_tko = `win_by_KO/TKO`,
         total_time_fought_seconds = `total_time_fought(seconds)`)

# Turning data relative to number of fights
fighter_profile_data <- fighter_profile_data %>% 
  mutate(win_by_Decision_Majority = win_by_Decision_Majority/wins,
         win_by_Decision_Split = win_by_Decision_Split/wins,
         win_by_Decision_Unanimous = win_by_Decision_Unanimous/wins,
         win_by_Submission = win_by_Submission/wins,
         win_by_ko_tko = win_by_ko_tko/wins,
         win_by_TKO_Doctor_Stoppage = win_by_TKO_Doctor_Stoppage/wins
         ) %>% 
  mutate(win_by_ko_tko = win_by_ko_tko + win_by_TKO_Doctor_Stoppage,
         win_by_Decision = win_by_Decision_Majority + win_by_Decision_Split + win_by_Decision_Unanimous) %>% 
  dplyr::select(-win_by_Decision_Majority, -win_by_Decision_Split, -win_by_Decision_Unanimous, -win_by_TKO_Doctor_Stoppage)
```

# K-Means Clustering of Fighters

```{r}
#Scaling the Data:
fighter_profile_data_reduced <- fighter_profile_data %>% 
  dplyr::select(Referee, #Do not Remove!
         date, #Do not Remove!
         location, #Do not Remove!
         fighter, #Do not Remove!
         Reach_cms, #Please change parameters to be included in clustering here
         Weight_lbs, 
         ends_with("_att"), 
         avg_REV, 
         avg_PASS, 
         avg_KD,
         win_by_Decision,
         win_by_ko_tko,
         win_by_Submission
         ) %>% 
  #what do avg_REV, avg_PASS, avg_KD measure??
  dplyr::select(-starts_with("avg_opp")) %>% 
  dplyr::select(-avg_TOTAL_STR_att, -avg_DISTANCE_att, -avg_SIG_STR_att) %>% 
  na.omit() #filtering all fighters with missing data

fighter_profile_data_scaled <- fighter_profile_data_reduced %>% 
  dplyr::select(-Referee, 
         -date, 
         -location,
         -fighter)
  
fighter_profile_data_scaled <- data.frame(scale(fighter_profile_data_scaled))
```

```{r EDA}
fighter_profile_data_scaled %>% 
  ggcorr(method = c("pairwise", "pearson"), layout.exp = 3,label_round=2, label = TRUE,label_size = 2,hjust = 1)

fviz_nbclust(fighter_profile_data_scaled, kmeans, method = "silhouette", k.max = 15) +
  labs(subtitle = "Silhouette method")
```

```{r}
model_km2 <- kmeans(fighter_profile_data_scaled, centers = 2, nstart = 50, iter.max = 100)
model_km3 <- kmeans(fighter_profile_data_scaled, centers = 3, nstart = 50, iter.max = 100)
model_km4 <- kmeans(fighter_profile_data_scaled, centers = 4, nstart = 50, iter.max = 100)
model_km5 <- kmeans(fighter_profile_data_scaled, centers = 5, nstart = 50, iter.max = 100)
```

```{r}
#add clusters to the data frame
fighter_profile_data_scaled_withClusters <- mutate(fighter_profile_data_scaled, cluster = as.factor(model_km2$cluster))

#First let's find the averages of the variables by cluster
center_locations <- fighter_profile_data_scaled_withClusters %>% 
  group_by(cluster) %>% 
  summarize_at(vars(Reach_cms:win_by_Submission),mean)

#Next I use gather to collect information together
xa2 <- gather(center_locations, key = "variable", value = "value", -cluster, factor_key = TRUE)

#Next I use ggplot to visualize centers
knnCenters <- ggplot(xa2, aes(x = variable, y = value)) + 
  geom_line(aes(color = cluster,group = cluster), linetype = "dashed",size=1) +
  geom_point(size=2,shape=4) + 
  geom_hline(yintercept=0) + 
  ggtitle("K-means centers k=2") + 
  labs(fill = "Cluster") + 
  theme(text = element_text(size=10),
        axis.text.x = element_text(angle=45,hjust=1),
        legend.title=element_text(size=5),
        legend.text = element_text(size=5)
  )
knnCenters

fviz_cluster(model_km2, fighter_profile_data_scaled, palette = "Set2", ggtheme = theme_minimal())

```

```{r}
#add clusters to the data frame
fighter_profile_data_scaled_withClusters <- mutate(fighter_profile_data_scaled, cluster = as.factor(model_km4$cluster))

#Your code here
#First let's find the averages of the variables by cluster
center_locations <- fighter_profile_data_scaled_withClusters %>% 
  group_by(cluster) %>% 
  summarize_at(vars(Reach_cms:win_by_Submission),mean)

#Next I use gather to collect information together
xa4 <- gather(center_locations, key = "variable", value = "value", -cluster, factor_key = TRUE)

#Next I use ggplot to visualize centers
knnCenters <- ggplot(xa4, aes(x = variable, y = value)) + 
  geom_line(aes(color = cluster,group = cluster), linetype = "dashed",size=1) +
  geom_point(size=2,shape=4) + 
  geom_hline(yintercept=0) + 
  ggtitle("K-means centers k=4") + 
  labs(fill = "Cluster") + 
  theme(text = element_text(size=10),
        axis.text.x = element_text(angle=45,hjust=1),
        legend.title=element_text(size=5),
        legend.text = element_text(size=5)
  )
knnCenters

fviz_cluster(model_km4, fighter_profile_data_scaled, palette = "Set2", ggtheme = theme_minimal())

```

```{r}
model_km2$size #3016 3626
model_km3$size #2300 2339 2003
model_km4$size #2052 1426 1460 1704
model_km5$size #1387 1215 1513 1356 1171
```

```{r}
g2 <- fviz_cluster(model_km2, fighter_profile_data_scaled, palette = "Set2", ggtheme = theme_minimal())
g3 <- fviz_cluster(model_km3, fighter_profile_data_scaled, palette = "Set2", ggtheme = theme_minimal())
g4 <- fviz_cluster(model_km4, fighter_profile_data_scaled, palette = "Set2", ggtheme = theme_minimal())
g5 <- fviz_cluster(model_km5, fighter_profile_data_scaled, palette = "Set2", ggtheme = theme_minimal())
grid.arrange(g2,g3,g4,g5)
```

##Combining the Data

The following code integrates the cluster in the original fighter-dataframe

```{r}
fighter_profile_data_reduced_withClusters <- mutate(fighter_profile_data_reduced, cluster = as.factor(model_km4$cluster)) 

temp <- fighter_profile_data_reduced_withClusters %>% 
  dplyr::select(Referee, date, location, fighter, cluster)

fighter_profile_data <- fighter_profile_data %>% 
  left_join(temp, by = c("fighter", "location", "date", "Referee")) %>% 
  mutate(new_fighter = ifelse(is.na(total_time_fought_seconds), 1,0),
         vet_but_no_wins = ifelse(!is.na(total_time_fought_seconds) & wins==0, 1, 0))
```

This is a sanity check. The function should always output 0: 

```{r}
length(fighter_profile_data$date[is.na(cluster)& fighter_profile_data$new_fighter==0&fighter_profile_data$vet_but_no_wins==0])
```



```{r}
total_fight_data <- read_delim("raw_total_fight_data.csv", delim = ";")
clean_names(total_fight_data)

total_fight_data <- total_fight_data %>% 
  mutate(date = mdy(date)) %>% 
  dplyr::select(-Winner, -Fight_type) %>% 
  left_join(fight_data, by = c("R_fighter", "B_fighter", "Referee", "date", "location")) %>% 
  mutate(women = ifelse(grepl("Women", weight_class), TRUE, FALSE))

total_fight_data_men <- total_fight_data %>% 
  subset(women == FALSE)

total_fight_data_women <- total_fight_data %>% 
  subset(women == TRUE)


```

```{r}
total_fight_data_men$R_cluster <- NA
total_fight_data_men$B_cluster <- NA

total_fight_data_men$R_cluster <- fighter_profile_data$cluster[match(paste(total_fight_data_men$location, total_fight_data_men$Referee, total_fight_data_men$date, total_fight_data_men$R_fighter), paste(fighter_profile_data$location, fighter_profile_data$Referee, fighter_profile_data$date, fighter_profile_data$fighter))]

total_fight_data_men$B_cluster <- fighter_profile_data$cluster[match(paste(total_fight_data_men$location, total_fight_data_men$Referee, total_fight_data_men$date, total_fight_data_men$B_fighter), paste(fighter_profile_data$location, fighter_profile_data$Referee, fighter_profile_data$date, fighter_profile_data$fighter))]

sum(is.na(total_fight_data_men$R_cluster)) #1141
sum(is.na(total_fight_data_men$B_cluster)) #1877
#3018

sum(is.na(fighter_profile_data$cluster)) #3014
```
```{r include=FALSE}
OPENCAGE_KEY="b240e0f7a927441ba1b345dae97c1ba5"
```

```{r}
library(maps)
library(maptools)   #mapping: plotting
library(rgeos)      #mapping: simplifying geometry
library(rgdal)      #mapping: projecting
library(spdep)      #Moran's I, Geary's C, poly2nb
library(rnaturalearth)
library(ggmap)
library(opencage)
library(sf)
library(gganimate)
library(hrbrthemes)

map_data <- total_fight_data_men %>% 
  group_by(location) %>% 
  summarise(count = n(),
         first_fight = min(date))

latitudes <- numeric(0)
longitudes <- numeric(0)
locations <- map_data$location

for (i in locations){
   temp = opencage_forward(i, key = OPENCAGE_KEY)
   lat = median(temp$results$geometry.lat)
   lng = median(temp$results$geometry.lng)
   latitudes[i] = lat
   longitudes[i] = lng
}

map_data <- map_data %>% 
  mutate(lat = latitudes,
         lng = longitudes)

world <- ne_countries(scale = "medium", returnclass = "sf") %>% 
  filter(name != "Antarctica")

plt <- ggplot(world) +
  geom_sf() +
  geom_point(data=map_data,
             aes(x=lng,
                 y=lat,
                 size=count,
                 color=first_fight,
                 group = seq_along(first_fight)))+
  labs(title = "The History of UFC: How fights have expanded globally over time")+
  theme(text=element_text(size = 13, family="Tahoma"))+
  transition_reveal(first_fight) +
  shadow_mark(alpha = 0.3, size = 0.5)
  
plt
```


```{r}
#Plot a distribution curve of how long each fight lasted, split by round format
# add last round time, total fight time
total_fight_data_men <- total_fight_data_men %>% 
  mutate(last_round_time = as.character(last_round_time),
         last_round_time = gsub('.{3}$', '', last_round_time),
         last_round_time = ms(last_round_time),
         total_fight_time = (last_round-1)*ms("05:00")+last_round_time,
         total_fight_time_sec = seconds(total_fight_time))

# total time = (last_round - 1) * 5 + (last_round time)
density_data <- total_fight_data_men %>% 
  mutate(no_of_rounds = as.factor(no_of_rounds))

vertical.lines <- c(300,600,900,1200,1500)
density <- ggplot(density_data, aes(x = total_fight_time_sec, color = no_of_rounds, fill = no_of_rounds)) + geom_density(alpha = 0.9) + geom_vline(xintercept = vertical.lines, linetype = "dotted", color = "orange", size = 0.5) +
  labs(title = "How long do the fights of different formats last?", x = "Fight Time (sec)", y = "Density", fill = "Round Format", color = "Round Format")+
  theme_light()+
  scale_fill_brewer(palette = "Accent")+
  scale_color_brewer(palette = "Accent")+
  theme(text=element_text(family="Tahoma"))
density

```


We now have 2 table: 

`total_fight_data_men` containing information on the fights.
`fighter_profile_data` containing information on the fighters (incl. the outcome of the clustering)

The two tables can be linked using the `Referee`, `location`, `date` and `fighter` column(s). 

ToDO:

*Parsing of columns in the total_fight_data table (eg. getting rid of "of"s in some columns)


## Visualizations

```{r}
# GGRadar Plot

# Data Processing before making a plot
cluster_radar <- center_locations %>% 
  mutate_each(funs(rescale), -cluster) %>% 
  rename("Arm Reach" = Reach_cms, "Weight(lbs)" = Weight_lbs, "Body" = avg_BODY_att, "Clinch" = avg_CLINCH_att, "Ground" = avg_GROUND_att,
         "Head" = avg_HEAD_att, "Leg" = avg_LEG_att, "Sub" = avg_SUB_ATT, "TD" = avg_TD_att, "REV" = avg_REV, "PASS" = avg_PASS, 
         "K/D" = avg_KD, "Decision" = win_by_Decision, "TKO or KO" = win_by_ko_tko, "Submission" = win_by_Submission) %>%
  mutate(cluster = as.numeric(cluster))

# rename clusters to our self-defined clusters
cluster_radar[1, 1] <- "Heavy Fighters"
cluster_radar[2, 1] <- "Submission Artists"
cluster_radar[3, 1] <- "Wrestlers"
cluster_radar[4, 1] <- "All-Rounders"

glimpse(cluster_radar)

# ggradar plot
ggradar_plot <- cluster_radar %>% 
  ggradar(font.radar = "Tahoma",
        background.circle.colour = "#D7D6D1",
        background.circle.transparency = 0.1,
        plot.legend = if (nrow(cluster_radar) > 1) TRUE else FALSE,
        legend.title = "Fighter Type",
        legend.text.size = 10,
        plot.title = "4 Clusters of UFC",
        group.point.size = 3,
        base.size = 14,
        plot.extent.x.sf = 1,
        plot.extent.y.sf = 1.2,
        grid.label.size = 5,
        axis.label.size = 3.5) #It would be nice if we can name the types of the fighters P!

plot(ggradar_plot)

# Individual Plots
ggRadar_plot <- ggRadar(data = cluster_radar, aes(color = cluster),legend.position = "none", interactive = FALSE, size = 1, rescale = FALSE, use.label = TRUE)+
  scale_y_discrete(breaks = NULL)+
  ggtitle("Stat by Each UFC Fighter Types")+
  theme(axis.text.x = element_text(size = 5))+
  scale_color_brewer(palette = "Set2")+
  scale_fill_brewer(palette = "Set2")+
  theme(text=element_text(size=13, family="Tahoma"))+
  facet_grid(~cluster)+
  theme(axis.text.x = element_text(vjust = 50, angle = -90-360/15*(1:15)))

plot(ggRadar_plot)

```


```{r}
fighter_data <- fighter_profile_data %>%
  dplyr::select(-Referee:-fighter) %>%
  na.omit()

fighter_data$Weight_lbs = as.factor(fighter_data$Weight_lbs)

fighter_data$Weight_lbs <- fct_collapse(fighter_data$Weight_lbs,
  '125' = ("125"),
  '135' = ("135"),
  '145' = ("145"),
  '155' = ("155"),
  '170' = c("168", "170"),
  '185' = ("185"),
  '205' = ("205"),
  heavy = c("225", "230", "231", "234", "235", "238", "240", "242", "243", "245", "247", "249", "250", "253", "255", "258",
             "260", "263", "264", "265"))


f6 <- fighter_data %>%
      group_by(cluster) %>%
    dplyr::summarise(number=dplyr::n())

f5 <- fighter_data %>%
  group_by(cluster, Weight_lbs) %>%
  dplyr::summarise(number=dplyr::n()) 


for (i in 1:8){
  f5$number[i] = f5$number[i]/2037
}


for (i in 9:16){
  f5$number[i] = f5$number[i]/1406
}


for (i in 17:24){
  f5$number[i] = f5$number[i]/1443
}


for (i in 25:32){
  f5$number[i] = f5$number[i]/1664
}


ggplot(f5, aes(x = cluster, y =number)) + 
geom_col(aes(fill = Weight_lbs))+
  theme_bw()+
  labs(title="Clusters and Weight Classes ",
       subtitle = "What are the proportion of different weight classes in each cluster?", 
       x = "Cluster Number",
       y = "Proportion of fighters")+
  theme(text=element_text(size=13, family="Tahoma"))+
  scale_fill_brewer(palette = "Greens")
  NULL





f5$Weight_lbs = as.factor(f5$Weight_lbs)


f5$Weight_lbs <- fct_collapse(f5$Weight_lbs,
  '125' = ("125"),
  '135' = ("135"),
  '145' = ("145"),
  '155' = ("155"),
  '170' = c("168", "170"),
  '185' = ("185"),
  '205' = ("205"),
  heavy = c("225", "230", "231", "234", "235", "238", "240", "242", "243", "245", "247", "249", "250", "253", "255", "258",
             "260", "263", "264", "265"))



f <- fighter_data %>%
  group_by(Weight_lbs) %>%
  dplyr::summarise(number=dplyr::n(),
              win_by_ko_tko= sum(win_by_ko_tko),
            win_by_Submission = sum(win_by_Submission),
            win_by_Decision = sum(win_by_Decision)) 

f$Weight_lbs = as.factor(f$Weight_lbs)


f$Weight_lbs <- fct_collapse(f$Weight_lbs,
  '125' = ("125"),
  '135' = ("135"),
  '145' = ("145"),
  '155' = ("155"),
  '170' = c("168", "170"),
  '185' = ("185"),
  '205' = ("205"),
  heavy = c("225", "230", "231", "234", "235", "238", "240", "242", "243", "245", "247", "249", "250", "253", "255", "258",
             "260", "263", "264", "265"))


f1 <- f %>%
  group_by(Weight_lbs) %>%
  dplyr::summarise(number = sum(number),
              win_by_ko_tko= sum(win_by_ko_tko),
            win_by_Submission = sum(win_by_Submission),
            win_by_Decision = sum(win_by_Decision)) 
  

for (i in 1:nrow(f1)){
  f1$win_by_ko_tko[i] = f1$win_by_ko_tko[i]/f1$number[i]*100
  f1$win_by_Submission[i] = f1$win_by_Submission[i]/f1$number[i]*100
  f1$win_by_Decision[i] = f1$win_by_Decision[i]/f1$number[i]*100
}

```
```{r}
f1_long <- gather(f1, win_type, percentage, win_by_ko_tko:win_by_Decision, factor_key=TRUE)

# Rename the values in the dataframe to make the legend more clear
levels(f1_long$win_type)[levels(f1_long$win_type) == "win_by_ko_tko"] <- "Win by KO/TKO"
levels(f1_long$win_type)[levels(f1_long$win_type) == "win_by_Submission"] <- "Win by Submission"
levels(f1_long$win_type)[levels(f1_long$win_type) == "win_by_Decision"] <- "Win by Decision"


ggplot(f1_long, aes(x = Weight_lbs, y =percentage)) + 
geom_col(aes(fill = win_type))+
  theme_bw()+
  labs(title="Win Type",
       subtitle = "Variation of win types between weigh classes", 
       x = "Weight Class",
       y = "Percentage of Wins",
       fill = "Win Type")+
  scale_fill_brewer(palette = "Paired")+
  theme(text=element_text(family="Tahoma"))+
  NULL

```

```{r}
#Calculating summery data for the cluster matchups
cluster_perfA <- total_fight_data_men %>% 
  group_by(R_cluster, B_cluster, Winner) %>% 
  summarise(fights = n()) 
cluster_perfB <- total_fight_data_men %>% 
  group_by(B_cluster, R_cluster, Winner) %>% 
  summarise(fights = n())

cluster_perfA <- cluster_perfA %>% 
  spread(key = Winner, value = fights) 
cluster_perfB <- cluster_perfB %>% 
  spread(key = Winner, value = fights)

library(tidyr)
cluster_perfA$Draw <- tidyr::replace_na(cluster_perfA$Draw, 0) 
cluster_perfB$Draw <- tidyr::replace_na(cluster_perfB$Draw, 0)

cluster_perfA <- cluster_perfA %>% 
  mutate(fights = Blue + Draw + Red) %>% 
  rename(fighterCluster=R_cluster,
         oppCluster=B_cluster,
         Wins=Red,
         Losses=Blue)
cluster_perfB <- cluster_perfB %>% 
  mutate(fights = Blue + Draw + Red) %>% 
  rename(fighterCluster=B_cluster,
         oppCluster=R_cluster,
         Wins=Blue,
         Losses=Red)

cluster_perf_incl_draws <- cluster_perfA %>% 
  left_join(cluster_perfB, by = c("fighterCluster", "oppCluster")) %>% 
  summarise(fights = (fights.x + fights.y),
            wins = (Wins.x + Wins.y),
            losses = (Losses.x + Losses.y),
            draws = (Draw.x + Draw.y)
            ) %>% 
  mutate(win_per = wins/fights,
         draw_per = draws/fights)

cluster_perf_excl_draws <- cluster_perfA %>% 
  left_join(cluster_perfB, by = c("fighterCluster", "oppCluster")) %>% 
  summarise(fights = (fights.x + fights.y - Draw.x - Draw.y),
            wins = (Wins.x + Wins.y),
            losses = (Losses.x + Losses.y)
            ) %>% 
  mutate(win_per = wins/fights)
```

```{r}
#Create Heatmap for Wins
dfWins <- cluster_perf_excl_draws %>% 
  dplyr::select(-fights, -wins, -losses) %>% 
  spread(key = oppCluster, value = win_per) 

#dfWins[1, 3:6] = NA
#dfWins[2, 4:6] = NA
#dfWins[3, 5:6] = NA
#dfWins[4, 6] = NA

dfWins <- dfWins %>% 
  gather(2:6, key = oppCluster, value = win_per)

dfWins$fighterCluster <- ifelse(is.na(dfWins$fighterCluster), 'newFighter', dfWins$fighterCluster)
dfWins$oppCluster <- ifelse(dfWins$oppCluster=="<NA>", 'newFighter', dfWins$oppCluster)

dfWins <- dfWins %>% 
  ungroup() %>% 
  mutate(fighterCluster = factor(fighterCluster, levels = c(1,2,3,4,"newFighter"))) %>% 
  group_by(fighterCluster) %>% 
  mutate(oppCluster = factor(oppCluster, levels = c(1,2,3,4,"newFighter")))
 
library(forcats)
ggplot(dfWins, aes(x = oppCluster, y = fct_rev(fighterCluster), fill = win_per)) +
  geom_tile()+
  geom_text(aes(label=round(win_per, digits=2)))+
  theme(text=element_text(size = 13, family="Tahoma"))+
  labs(
    title = "Heatmap for Probability of Win",
    x = "Opponent Cluster",
    y = "Fighter Cluster",
    fill = "Probability of Win (%)"
  )+
  NULL
```

```{r}
#Create Heatmap for Draws
dfDraws <- cluster_perf_incl_draws %>% 
  dplyr::select(-fights, -wins, -losses, -draws, -win_per) %>% 
  spread(key = oppCluster, value = draw_per) 

#dfDraws[1, 3:6] = NA
#dfDraws[2, 4:6] = NA
#dfDraws[3, 5:6] = NA
#dfDraws[4, 6] = NA

dfDraws <- dfDraws %>% 
  gather(2:6, key = oppCluster, value = draw_per)

dfDraws$fighterCluster <- ifelse(is.na(dfDraws$fighterCluster), 'newFighter', dfDraws$fighterCluster)
dfDraws$oppCluster <- ifelse(dfDraws$oppCluster=="<NA>", 'newFighter', dfDraws$oppCluster)

dfDraws <- dfDraws %>% 
  ungroup() %>% 
  mutate(fighterCluster = factor(fighterCluster, levels = c(1,2,3,4,"newFighter"))) %>% 
  group_by(fighterCluster) %>% 
  mutate(oppCluster = factor(oppCluster, levels = c(1,2,3,4,"newFighter")))
 
ggplot(dfDraws, aes(x = oppCluster, y = fct_rev(fighterCluster), fill = draw_per)) +
  geom_tile()+
  geom_text(aes(label=round(draw_per, digits=3)))+
  theme(text=element_text(size = 13, family="Tahoma"))+
  labs(
    title = "Heatmap for Probability of Draws",
    x = "Opponent Cluster",
    y = "Fighter Cluster",
    fill = "Probability of Draws (%)"
  )+
  NULL
```

```{r}
#Calculating summery data for average fight time
cluster_timeA <- total_fight_data_men %>% 
  filter(no_of_rounds==3) %>% #filter for modern standart duration only
  group_by(R_cluster, B_cluster) %>% 
  summarise(avg_length = mean(total_fight_time_sec),
            fights = n()) %>% 
  rename(fighterCluster=R_cluster,
         oppCluster=B_cluster)
cluster_timeB <- total_fight_data_men %>% 
  filter(no_of_rounds==3) %>% #filter for modern standart duration only
  group_by(B_cluster, R_cluster) %>% 
  summarise(avg_length = mean(total_fight_time_sec),
            fights = n()) %>% 
  rename(fighterCluster=B_cluster,
         oppCluster=R_cluster)

cluster_time <- cluster_timeA %>% 
  left_join(cluster_timeB, by = c("fighterCluster", "oppCluster")) %>% 
  mutate(avg_length = ((avg_length.x * fights.x) + (avg_length.y * fights.y)) / (fights.x + fights.y),
         fights = fights.x + fights.y) %>% 
  dplyr::select(-avg_length.x, -fights.x, -avg_length.y, -fights.y)
  

dfTime <- cluster_time %>% 
  dplyr::select(-fights) %>% 
  spread(key = oppCluster, value = avg_length) 

#dfTime[1, 3:6] = NA
#dfTime[2, 4:6] = NA
#dfTime[3, 5:6] = NA
#dfTime[4, 6] = NA

dfTime <- dfTime %>% 
  gather(2:6, key = oppCluster, value = avg_length)

dfTime$fighterCluster <- ifelse(is.na(dfTime$fighterCluster), 'newFighter', dfTime$fighterCluster)
dfTime$oppCluster <- ifelse(dfTime$oppCluster=="<NA>", 'newFighter', dfTime$oppCluster)

dfTime <- dfTime %>% 
  ungroup() %>% 
  mutate(fighterCluster = factor(fighterCluster, levels = c(1,2,3,4,"newFighter"))) %>% 
  group_by(fighterCluster) %>% 
  mutate(oppCluster = factor(oppCluster, levels = c(1,2,3,4,"newFighter"))) 

dfTime$avg_length <- seconds(round(dfTime$avg_length))
#dfTime$avg_length <- ms(dfTime$avg_length)
 
ggplot(dfTime, aes(x = oppCluster, y = fct_rev(fighterCluster), fill = avg_length)) +
  geom_tile()+
  geom_text(aes(label=round(avg_length, digits=3)))+
  theme(text=element_text(size = 13, family="Tahoma"))+
  labs(
    title = "Heatmap of Average Fight Time",
    x = "Opponent Cluster",
    y = "Fighter Cluster",
    fill = "Avergae Fight Time (sec)"
  )+
  NULL
```
